### 2014-11-04 evaluation.tex
Added RUBiS results

\begin{itemize}

\item \textbf{LWW register}: A last-write-wins register that provides read and
write operations. Each write is associated with a timestamp, which is used to
resolve conflicting concurrent writes -- newer write wins.

@@

\item \textbf{RuBis}: An ebay-like auction site~\cite{}. The application allows
users to browse items, bid for items on sale, and pay for items from a wallet
modelled after a bank account.

\item \textbf{Microblog}: A twitter-like microblogging site, modelled after
Twissandra~\cite{}. The application allows adding a new user, adding and
replying to tweets, following, unfollowing and blocking users, and fetching a
user's timeline, userline, followers and following.

\end{itemize}

\begin{table}
\setlength{\tabcolsep}{4pt}
{\sffamily \small
\begin{center}
\begin{tabular} {|l|r|r|r|r|r|r|r|r|}
\hline
{\bf Benchmark} & {\bf LOC} & {\bf \#T} & {\bf EC} & {\bf CC} & {\bf SC} & {\bf RC} & {\bf MAV} & {\bf RR} \\
\hline
{LWW Reg} & 108 & 1 & 2 & 2 & 2 & 0 & 0 & 0 \\
{DynamoDB} & 126 & 1 & 3 & 1 & 2 & 0 & 0 & 0 \\
{Bank Account} & 155 & 1 & 1 & 1 & 1 & 1 & 0 & 1 \\
{Shopping List} & 140 & 1 & 2 & 1 & 1 & 0 & 0 & 0 \\
{Online store} & 340 & 4 & 9 & 1 & 0 & 2 & 0 & 1 \\
{Rubis} & 640 & 6 & 14 & 2 & 1 & 4 & 2 & 0 \\
{Microblog} & 659 & 5 & 13 & 6 & 1 & 6 & 3 & 1 \\
\hline
\end{tabular}
\end{center} }
\caption{The distribution of classfied contracts. \#T refers to the number of
tables in the application. The columns 4-6 (7-9) represent operations
(transactions) assigned to this consistency (isolation) level.}
\label{tab:ctrts}
\end{table}

@@

\begin{figure*}
  \centering
  \subfigure[Bank account latency]{\label{grf:BA-lat}\includegraphics[width=0.252\textwidth]{graphs/BA-lat.pdf}}
  \subfigure[Bank account throughput]{\label{grf:BA-tp}\includegraphics[width=0.24\textwidth]{graphs/BA-tp.pdf}}
  \subfigure[LWW transactions]{\label{grf:LWW-txn}\includegraphics[width=0.24\textwidth]{graphs/LWW-txn.pdf}}
  \subfigure[Impact of summarization]{\label{grf:summarization}\includegraphics[width=0.235\textwidth]{graphs/summarization.pdf}}
	\caption{Quelea Performance.}
  \label{grf:LWW_perf}
\end{figure*}

Figure~\ref{grf:BA-lat} and~\ref{grf:BA-tp} analyzes the latency and throughput
of operations in bank account example as we increase the number of clients in
\cf{1DC} configuration. Our client workload was generated using YCSB
benchmark~\cite{}. The benchmark uniformly chose from 100,000 keys, where the
operation spread was 25\% withdraw, 25\% deposit and 50\% getBalance, which
corresponds to the default 50:50 read:write mix in YCSB. Here, the lines marked
EC and CC correspond to all operations being assigned EC and CC consistency
levels. These levels compromise correctness as withdraw has to be and SC
operation. The line SC corresponds to a configuration where all operations are
strongly consistent; this ensures application correctness. \name corresponds to
our implementation, which classifies operations based on their contracts.

Both \name and SC ensure correctness. However, with 512 clients, \name
implementation was within 41\% of latency and 18\% of throughput of EC, whereas
SC operations had 162\% higher latency and 52\% lower throughput than EC
operations. In \cf{2DC} configuration (not-shown), the average latency of SC
operations with 512 clients increased by 9.4$\times$ due to the cost of
geo-distributed coordination, whereas \name operations were only 2.2$\times$
slower, mainly due to the increased cost of \cf{withdraw} operations.
Importantly, the latency of \cf{getBalance} and \cf{deposit} remained almost
the same. This illustrates the benefit of fine-grained contract classification
in \name.

@@

We also compared the performance of EC LWW operations directly against
Cassandra (our backing store), which uses last-writer-wins as the only
convergence semantics. While Cassandra provides no stronger-than-eventual
consistency properties, \name was within 30\%(20\%) of latency(throughput) of
Cassandra with 512 clients, illustrating that the programmers only have to pay
a minimal overhead for the expressive and stronger \name programming model.

>>>>

\begin{itemize}
\setlength{\itemsep}{2pt}
\item \textbf{LWW register}: A last-write-wins register that provides read and
write operations. Each write is associated with a timestamp, which is used to
resolve conflicting concurrent writes -- newer write wins.

@@

\item \textbf{RUBiS}: An ebay-like auction site~\cite{}. The application allows
users to browse items, bid for items on sale, and pay for items from a wallet
modelled after a bank account.

\item \textbf{Microblog}: A twitter-like microblogging site, modelled after
Twissandra~\cite{}. The application allows adding a new user, adding and
replying to tweets, following, unfollowing and blocking users, and fetching a
user's timeline, userline, followers and following.
\end{itemize}

\begin{table}
\setlength{\tabcolsep}{4pt}
{\sffamily \small
\begin{center}
\begin{tabular} {|l|r|r|r|r|r|r|r|r|}
\hline
{\bf Benchmark} & {\bf LOC} & {\bf \#T} & {\bf EC} & {\bf CC} & {\bf SC} & {\bf RC} & {\bf MAV} & {\bf RR} \\
\hline
{LWW Reg} & 108 & 1 & 2 & 2 & 2 & 0 & 0 & 0 \\
{DynamoDB} & 126 & 1 & 3 & 1 & 2 & 0 & 0 & 0 \\
{Bank Account} & 155 & 1 & 1 & 1 & 1 & 1 & 0 & 1 \\
{Shopping List} & 140 & 1 & 2 & 1 & 1 & 0 & 0 & 0 \\
{Online store} & 340 & 4 & 9 & 1 & 0 & 2 & 0 & 1 \\
{RUBiS} & 640 & 6 & 14 & 2 & 1 & 4 & 2 & 0 \\
{Microblog} & 659 & 5 & 13 & 6 & 1 & 6 & 3 & 1 \\
\hline
\end{tabular}
\end{center} }
\caption{The distribution of classfied contracts. \#T refers to the number of
tables in the application. The columns 4-6 (7-9) represent operations
(transactions) assigned to this consistency (isolation) level.}
\label{tab:ctrts}
\end{table}

@@

\begin{figure*}
  \centering
  \subfigure[Bank account]{\label{grf:BA-tp-vs-lat}\includegraphics[width=0.24\textwidth]{graphs/BA-tp-vs-lat.pdf}}
  \subfigure[LWW transactions]{\label{grf:LWW-txn}\includegraphics[width=0.24\textwidth]{graphs/LWW-txn.pdf}}
  \subfigure[RUBiS bidding mix]{\label{grf:rubis}\includegraphics[width=0.24\textwidth]{graphs/Rubis.pdf}}
  \subfigure[Impact of summarization]{\label{grf:summarization}\includegraphics[width=0.235\textwidth]{graphs/summarization.pdf}}
	\caption{Quelea Performance.}
  \label{grf:LWW_perf}
\end{figure*}

Figure~\ref{grf:BA-tp-vs-lat} shows the throughtput vs. latency of operations
in bank account example as we increase the number of clients in \cf{1DC}
configuration. Our client workload was generated using YCSB benchmark~\cite{}.
The benchmark uniformly chose from 100,000 keys, where the operation spread was
25\% withdraw, 25\% deposit and 50\% getBalance, which corresponds to the
default 50:50 read:write mix in YCSB. We increased the number of clients from
128 to 1024, and each experiment ran for 180 seconds.

The lines marked EC and CC correspond to all operations being assigned EC and
CC consistency levels. These levels compromise correctness as withdraw has to
be and SC operation. The line SC corresponds to a configuration where all
operations are strongly consistent; this ensures application correctness. \name
corresponds to our implementation, which classifies operations based on their
contracts. Both \name and SC ensure correctness. However, with 512 clients,
\name implementation was within 41\% of latency and 18\% of throughput of EC,
whereas SC operations had 162\% higher latency and 52\% lower throughput than
EC operations. Observe that there is a point in each case after which the
latency increases while the throughput decreases. This indicates a point after
which the store becomes saturated with client requests.

In \cf{2DC} configuration (not-shown), the average latency of SC operations
with 512 clients increased by 9.4$\times$ due to the cost of geo-distributed
coordination, whereas \name operations were only 2.2$\times$ slower, mainly due
to the increased cost of \cf{withdraw} operations. Importantly, the latency of
\cf{getBalance} and \cf{deposit} remained almost the same. This illustrates the
benefit of fine-grained contract classification in \name.

@@

We also compared (not shown) the performance of EC LWW operations directly
against Cassandra (our backing store), which uses last-writer-wins as the only
convergence semantics. While Cassandra provides no stronger-than-eventual
consistency properties, \name was within 30\%(20\%) of latency(throughput) of
Cassandra with 512 clients, illustrating that the programmers only have to pay
a minimal overhead for the expressive and stronger \name programming model.

Figure~\ref{grf:rubis} compares the \name implementation of RUBiS in \cf{1DC}
configuration against a single replica (NoRep) and strongly replicated
(StrongRep) \cf{1DC} deployment. The benchmark was RUBiS bidding mix, which has
15\% read-write interactions, which is representative of the auction workload.
Without replication, NoRep trivially provides strong consistency. However, this
deployment does not scale beyond 1750 operations per second. Strong replication
offers better throughput at the cost of greater latency due to inter-replica
coordination. \name deployment offers the benefit of replication, while only
paying the cost of coordination when necessary.
